Boundary Labeling for annotated documents

### 2017-07-05 LaTeX/Paper.tex
Extended Paper. No changes to Code.

%opening
\title{<TITLE PENDING>}
\author{
 \authorname{Jakob Klinger} \\
 \studentnumber{1125755} \\
 \curriculum{033 534} \\
 \email{e1125755@student.tuwien.ac.at}
}

@@

%TODO: Abstract (\begin{abstract}...\end{abstract}

@@

%TODO: Was genau wollen wir erreichen?
%TODO: Sektion: Terminologie

>>>>

%opening
\title{Boundary Labeling for annotated documents}%Vielleicht genauerer Titel?
\author{
 \authorname{Jakob Klinger} \\
 \studentnumber{1125755} \\
 \curriculum{033 534} \\
 \email{e1125755@student.tuwien.ac.at}
}

@@

%TODO: Abstract: \begin{abstract}...\end{abstract}

@@

\section{Boundary Labeling}
Boundary Labeling can be explained very quickly -  connect a Point of Interest with a box containing further information which is located outside of the main area. To easily reference important concepts, some additional Terminology will be introduced:

\begin{itemize}
\item \textbf{Label:} The additional information, usually represented as a box containing the additional information. Will also be referred to as \textbf{``Annotation''} in this paper.
\item \textbf{Site:} The point, object or word that is labeled - without it, there wouldn't be any labeling necessary.%Is that the correct name?
\item \textbf{Leader:} The line connecting the site to the label - depending on its shape, it can be further classified into several subgroups.
\end{itemize}

\subsection{Boundary Labeling in Documents}
As with other labeling techniques, Boundary Labeling has guidelines on how to create an optimal labeling - the leaders should be as direct as possible, no important information should be obscured, and it should be easily discernable which Label belongs to which site. These three often stand in conflict with one another, especially when labeling documents, as the text usually is very dense and leaves little space for leaders in between, yet one shouldn't allow them to pass through the text, as this makes the text harder to read.

%TODO: Über bisherige Versuche/Papers sprechen
%TODO: Was genau wollen wir erreichen?
%TODO: Sektion: Terminologie
